% ______________________________________________________________________________
%
%   2DV603 Software Engineering
%   Assignment 1 --- Requirements Engineering
%
%   Author:  Jonas Sjöberg
%            Linnaeus University
%            js224eh@student.lnu.se
%            github.com/jonasjberg
%            www.jonasjberg.com
%
%  License:  Creative Commons Attribution 4.0 International (CC BY 4.0)
%            <http://creativecommons.org/licenses/by/4.0/legalcode>
%            See LICENSE.md for additional licensing information.
% ______________________________________________________________________________


\section{Domain Analysis Document}
Task description from the assignment instructions
\cite{2dv603:assignment1-instructions}:

\begin{quote}
  Develop a full requirements definition for the above problem. Among the
  techniques you should consider employing are the following: 1) take a look at
  existing front-desk systems; 2) write scenarios; 3) derive use cases; 4)
  perform use case analysis, to determine who the actors are and what tasks
  they must perform; 5) narrow the problem statement, excluding features that
  will not be needed in the first release.
\end{quote}


\subsection{Scenarios}
%
% TODO: Write scenarios..
%
\subsubsection{Potential guest inquires about future patronage}\label{scenario1}
%
% clerk asks about:
%     * stay which nights?
%     * which type of room do they want?
%
% System must:
%
%   * verify if room(s) are available on those nights before allowing a reservation to be made
%   * verification procedure must take less than 2 seconds to complete.
%   * allow requests for specific rooms, controlled by the manage
%
\begin{itemize}
  \item A travelling salesman needs somewhere to stay for one night a couple of
    weeks from now.  This person contacts the hotel by phone to inquire about
    vacancy over a couple of days.  
    
  \item The hotel personnel answers any questions and uses the management
    system to find out if any rooms are available in the requested time frame.
    The hotel employee relays information about which rooms are available.

  \item After hearing about the rooms, the salesman asks about room sizes.

  \item The employee looks up relevant characteristics and attributes and
    relays the information.

  \item After brief contemplation, the salesman decides to make a reservation
    for one of the vacant rooms. 
\begin{end}


\subsubsection{Guest checks in at the hotel}\label{scenario2}
% 
% * guest checks in
% 
%     * room is allocated until checkout
%     * must take in average less than 60 seconds to complete
% 
\begin{itemize}\label{scenario1}
  \item A travelling salesman arrives at the hotel after having sold nothing and has no patience for delays and pleasantries.
    He walks up to the hotel front desk and declares that he has made a reservation in advance and would like to check  in.
    
  \item The receptionist scrambles to find which room number the guest
    ostensibly has reserved. The receptionist asks the salesman for personal information used when making the reservation.

  \item The salesman provides personal information to the receptionist.
      
  \item The receptionist enters the information into the management system.
    After narrowing down the search results to a single number, the
    receptionist can retrieve the room key and proceed to guide the guest
    to his room.

  \item The salesman is provided with his room key and instructions on where
      the room is located.
\begin{end}


\subsubsection{Guest cancels a reservation}\label{scenario3}
% 
% * guest wishes to cancel a reservation:
% 
%     * reservation can be canceled at any time but a percentage of the room
%       price may be charged if the cancelation is done too late
% 
\begin{itemize}\label{scenario1}
  \item A cat named Gibson wishes to cancel a reservation due to feline matters.
    Gibson logs in to the hotel website using a identifier and access key that
        was provided to him when the room was first reserved.

  \item The web portal loads in under 2 seconds, which is considered good
      enough for a modern website. Gibson cries in cat but acknowledges that
        everything is really slow now and the hotel web portal is comparably
        performant.

  \item After clicking on clearly visible ``cancel reservation'' link, a
      message informs Gibson about the cancellation fee, calculated from the
        room price and time delta from planned residence and cancellation.
      
  \item Gibson sighs in cat and clicks the ``I Agree'' link, which leads to a
      confirmation page with a summary of upayments that will be billed.
\begin{end}



* overall guests

  system must:
    * record basic information about each guest, 
        * name, address, telephone number, credit card, passport number
    * keep track of the guests account
    * print guests bill.



\subsection{Use Cases}
%
%
% TODO: Derive uses cases..
%


\subsection{Use Case Analysis}
%
% TODO: Perform use case analysis to determine who the actors are and what tasks they must perform..
%


\subsection{Refined Problem Statement}
%
% TODO: Narrow the problem statement, excluding features that will not be needed in the first release ..
%
